Hypertension and microbiome

### 2019-01-01 rrbiome.Rmd
Cleaning adonis output

```{r function for adnoiscalculation, include = FALSE}
calculateadonis <- function(dset,
                            matrix,
                            responses = list(model_1 = "MAP", model_2 = "SYSTM", model_3 = "DIASM",
                                          model_4 = "PULSEPRESSURE", model_5 = "HYPERTENSION"),
                            covariates = "BL_AGE + SEX",
                            modelstring = "matrix ~ %s + %s",
                            npermutations = 99) {
    glmlist <- mclapply(responses, function(response) {
        fo <- as.formula(sprintf(modelstring, response, covariates))
        ad <- adonis(fo, data = dset, permutations = npermutations)
        ad$aov.tab %>% as.data.frame
    }, mc.cores = length(responses)) 
}
```

@@

```{r adonis3, eval = FALSE}

ret

 adonis.species <- calculateadonis(dset = meta(pseq.species),
                    matrix = bray.dist.m.species,
                    covariates = "BL_AGE + SEX",
                    npermutations = 92)

adonis(bray.dist.m.species ~ MAP + BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09,
       data = meta(pseq.species),
       permutations = 2)$aov.tab %>%
                            as.data.frame %>%
                            kable

 glmlist <- lapply(responses, function(response) {
        fo.family <- ifelse(length(unique(pull(dset, response))) > min_n_for_continuous, stats::gaussian, stats::binomial)
        fo <- sprintf(modelstring, response)
        stats::glm(formula = as.formula(fo), family = fo.family, data = dset) %>%
            broom::tidy() %>%
                dplyr::filter(grepl("diversities_", term)) %>%
                dplyr::mutate(response = response, fo = fo) %>%
                dplyr::select(-term)
    })
```

>>>>

```{r function for adnoiscalculation, include = FALSE}
calculateadonis <- function(dset,
                            matrix,
                            responses = list(model_1 = "MAP", model_2 = "SYSTM", model_3 = "DIASM",
                                          model_4 = "PULSEPRESSURE", model_5 = "HYPERTENSION"),
                            covariates = "BL_AGE + SEX",
                            modelstring = "matrix ~ %s + %s",
                            npermutations = 99) {
    ret  <- mclapply(responses, function(response) {
        fo <- as.formula(sprintf(modelstring, response, covariates))
        ad <- adonis(fo, data = dset, permutations = npermutations)
        ad$aov.tab %>% as.data.frame %>%
            tibble::rownames_to_column(var = "response") %>%
            dplyr::mutate(fo = fo)
    }, mc.cores = length(responses))
    data.table::rbindlist(ret, id = "model_name") 
}
```

@@

```{r adonis3, eval = FALSE}
adonis.species %>%
    broom::tidy()

ret <- list(model_1 = adonis.species$model_1 %>% tibble::rownames_to_column(var = "response"),
     model_2 =  adonis.species$model_2 %>% tibble::rownames_to_column(var = "response"))

data.table::rbindlist(ret, id = "model_name") %>%
    dplyr::filter(response %in% c("MAP", "SYSTM"))

    })
```
